Multi-Task Mutual Learning for Vehicle Re-Identification

### 2019-05-08 paper.tex
Add Aytac and Sean's changes.

%%%%%%%%% ABSTRACT
\begin{abstract}
Vehicle re-identification (Re-ID) aims to search a specific vehicle
instance across non-overlapping camera views.
%
The main challenge of vehicle Re-ID is that
the visual appearance of vehicles may drastically changes
according to diverse viewpoints and illumination.
%
Most of existing vehicle Re-ID model cannot make full use of
various complementary vehicle information, like vehicle identification and orientation.
%
In this paper, we propose a novel {\em Multi-Task Mutual Learning} (MTML) deep model
to learn discriminative feature simultaeously from multiple branches.
%
Specially, we design a consensus learning loss function by fusing feature of the final convolutional feature maps from all branches.
%
Extensive comparative evaluations demonstrate the effectiveness of the
proposed MTML method in comparison to the state-of-the-art vehicle Re-ID techniques on the two existing benchmarks
(VehicleID and VeRi-776).
We also get a competitive result on NVIDIA 2019 AI City Challenge Track 2.
\end{abstract}

@@

%% Background of vehicle Re-ID
With the development of autonomous driving
and smart city applications, the need for accurately analyzing vehicles in these
scenarios with related computer vision tasks \ie detection, classification and
pose estimation as well as re-identification is ever-increasing.
%
Specially, vehicle re-identification attracted increasing attentions in community
\cite{liu2016vehicleid,liu2016veri,liu2016veri,
wang2017orientation,Wang_2017_ICCV,Zhou2018VAMI},
since it can play an important role in
intelligent transportation system and social safety.

%% What's vehicle Re-ID?
Vehicle re-identification (Re-ID) aims at searching a specific vehicle
instance across non-overlapping camera views.
%
Due to the unavailability of license plate under some circumstances,
vehicle Re-ID by visual appearance is of great practical value in real-world applications such as smart cities.
%
This task is similar with a more popular task: person re-identification
\cite{gong2014re,chen2018person,Li2018Harmonious,xiao2016learning,
li2017person,wei2018person,song2018mask,chang2018multi,
shen2018deep,zhang2017deep,shen2018person,suh2018part},
but with more challenges:
%% Vehicle Re-ID challenges
(1) Unlike person Re-ID, pose/orientation of vehicles results in occlusion and drastic visual geometry changes, since vehicle is a kind of rigid body.
% The same vehicle under different viewpoints are visually more diverse than person,
This means that the same identity must be inferred with any pose/orientation of the vehicle is given.
(2) Even the same orientation, the different identity vehicles may look very similar
due to the similar even same vehicle model. This requires vehicle Re-ID models
to have a more powerful fine-grained recognition ability.

% Existing work's problem
Most of vehicle Re-ID methods \cite{liu2016vehicleid,liu2016veri,Shen_2017_ICCV,Zhou2018VAMI}
focus on using a single branch
to learn an embedding feature for vehicle instance re-identification
from the original information (e.g. the original whole vehicle image)
%
Due to the previously metioned challenges for vehicle re-identification,
this single branch structure can not take advantage of the diversity of vehicles.
%
On the other hand, most existing work
\cite{liu2016vehicleid,liu2016veri}
train vehicle Re-ID deep learning model
by using a single supervisory signal (like vehicle ID).
%
However, vehicle ID label can not reflect the two kind of differences between vehicle instances:
(1) the vehicles with the same ID under different viewpoints,
(2) the vehicles with the different IDs under the same viewpoints.
Therefore, combining multiple supervisory signals (e.g. vehicle ID and vehicle orientation) together can be effective for vehicle Re-ID model learning.

\begin{figure}
%  \includegraphics[width=\linewidth,trim=0cm 8cm 0cm 0cm,clip=true]{images/system_overview_orient_only.pdf}
  \caption{A comparision of the same vehicle ID and different ID.}
	\label{F:veh_comparison}
\end{figure}

% Our contributions
In this work, we propose a novel {\em Multi-Task Mutual Learning}
(MTML) based network architecture,
that aims to simultaneously learn a number of tasks from supervisory signals, plus a consensus loss function, to build an improved representation for the purpose of vehicle re-identification.

These two contributions of our work are highlighted as follows:
(1) we formulate a novel {\em Multi-Task Mutual Learning} (MTML) deep learning model by building an individual branch for each task for vehicle Re-ID.
A multi-branch structure is designed for learning different tasks, such as vehicle ID, multi-scale, grayscale, and orientation.
It aims to discover and capture concurrently complementary discriminative information.
(2) We introduce a mutual learning mechanism for improving multi-label learning robustness.
It makes our learning model can benefit from multiple supervisory signals, and then learn the discrimative features for vehicle Re-ID.
%(3) we propose a cross-dataset joint learning framework for vehicle Re-ID.
Extensive comparative evaluations demonstrate the effectiveness of the
proposed MTML method in comparison to the state-of-the-art vehicle Re-ID techniques on the two existing benchmarks
(VehicleID \cite{liu2016vehicleid} and VeRi-776 \cite{liu2016veri}).
We also get a competitive result on CityFlow \cite{tang2019cityflow} benchmark at NVIDIA 2019 AI City Challenge.

@@

\noindent {\bf Vehicle Model Classification }
One closely related problem to re-identification is vehicle model
classification
\cite{liao2015exploiting,yang2015compcars,sochor2016boxcars,hu2017deep}.
But, the two problems are usually studied independently.
For example, Yang et al. \cite{yang2015compcars} propose a part attributes driven
vehicle model recognition.
They also contribute a large comprehensive car dataset named ``CompCars''
with model class labels but without vehicle identity labels.
More recently, Hu et al. \cite{hu2017deep} formulate a deep CNN framework capable of
selecting spatial salient vehicle parts in order to learn more
discriminative model representations without explicit parts annotations, with

\noindent {\bf Vehicle Re-Identification. }
%Whist vehicle Re-ID is less studied than person Re-ID
%\cite{gong2014person,li2018harmonious,zhong2017camera},
%there are a handful of existing methods.
%Notably, Feris \etal \cite{feris2012large} proposed an attribute-based Re-ID method.
%The vehicles are firstly classified by different attributes like car model types and colours. The Re-ID matching is then conducted in the attribute space.
%%
%Dominik \etal \cite{zapletal2016vehicle}
%used 3D bounding boxes for rectifying car images and then concatenate colour histogram features of vehicle image pairs.
%A binary linear SVM model is then trained to verify whether a pair of images have the same identity.
%%
%Both methods rely heavily on weak hand-crafted visual features in a
%complex multi-step based approach, suffering from weak discriminative model generalisation.
Recently, deep learning techniques have been exploited to vehicle Re-ID.  Liu
\etal \cite{liu2016veri} explored a deep neural network to estimate the
visual similarities between vehicle images.
%Vehicle appearances, spatio-temporal information and license plates are
%independently and incrementally used to improve the similarity function for
%vehicle matching.  they use a deep neural network to estimate the visual
%similarities between vehicle images for enjoying the strong representation
%learning capacity.
%
Liu \etal \cite{liu2016vehicleid} also designed a Coupled Clusters Loss (CCL)
to boost a multi-branch CNN model for vehicle Re-ID.
%
All these methods utilize the global appearance features of vehicle images and
ignore local discriminative regions.
%
To explore local information and motivated by the idea of landmark alignment
\cite{zhang2014facial} in both face recognition \cite{taigman2014deepface} and
human body pose estimation \cite{newell2016stacked}, Wang \etal
\cite{Wang_2017_ICCV} considered 20 vehicle keypoints for learning and aligning
local regions of a vehicle for Re-ID.  Clearly, this approach comes with extra
cost of exhaustively labeling these keypoints in a large number of vehicle
images, and the implicit assumption of having sufficient image
resolution/details for computing these keypoints.
%

@@

\noindent{\bf Multi-Task Learning. }
Multi-task learning (MTL) is a machine learning strategy
that learns several related tasks simultaneously for
their mutual benefits \cite{argyriou2007multi}. %  \cite{evgeniou2004regularized,ando2005framework,argyriou2007multi}.
A good MTL survey with focus on neural networks
is provided in \cite{caruana1997multitask}.
%
Deep CNNs are well suited for
performing MTL as they are inherently designed to learn joint
feature representations subject to multiple label objectives
concurrently in multi-branch architectures.
%
Joint learning of multiple related tasks
has been proven to be effective in solving computer vision problems
\cite{dong2017multi,zhang2016learning}.
% \cite{dong2017multi,zhang2016learning,ahmed2008training}.
%
Critically, our method is uniquely designed to
explore the potential of MTL
in combining multiple diversities (e.g. scale and color) of the vechile image
and being supervised by multiple kinds of manual labels (e.g. ID and orientation).
Each of them is associated with an individual branch of learning model.

@@

An overview of our proposed model can be seen in Figure \ref{F:overview}. The model is composed of a number of sub-branches, each of which is simultaneously learning a representation to solve its own set of tasks. In addition, there is a single fusion branch, which allows feature selection to be performed from the entire collection of individual representations. It is the output from this branch that is taken during deployment. Each sub-branch will now be described in more detail.

@@

In order to encourage the model to focus on details of the vehicles, that allow for separation of highly similar identity classes, we ensure that one branch will be unable to use colour information for distinguishing between these classes. This is simply done by giving as input only the grayscale image, and again training the branch to predict identity via the cross entropy loss.

@@

This branch is tasked with learning a representation to simultaneously predict the identity class and the orientation class, for examples for which this is known.
%In the case where the training images do not have associated orientation labels, this branch is trained in exactly the same way as the Vehicle Identity branch outlined above.
Both sets of labels are simultaneously employed in a joint loss function in order to optimise the branch for prediction of both identity and orientation. As orientation labels are not available for all training data, we employ a selective classifcation subset loss function, that allows the loss to be calculated across only the subset of the batch for which orientation labels are known.

@@

\begin{table*}
  \centering
  \begin{tabular}{c || c | c | c || c | c || c | c}
    \hline
    \multirow{2}{*}{Dataset} & \multicolumn{3}{c||}{Training} & \multicolumn{2}{c||}{Probe} & \multicolumn{2}{c}{Gallery} \\
    \cline{2-8}
    & \#IDs& \#Imgs & \#Orients & \#IDs & \#Imgs & \#IDs & \#Imgs \\
    \hline
    VeRi-776 \cite{liu2016veri}
    & 576 & 30188 & 8 & 200 & 1678 & 200 & 11579 \\
    VehicleID \cite{liu2016vehicleid}
    & 13164 & 100182 & - & 2400 & 17638 & 2400 & 2400 \\
%    BoxCars \cite{} & 21250 & 63750 & -  & - & - & - & - \\
%    CompCars \cite{} & 1118 & 31148 & - & - & - & - & - \\
    AICity2019 \cite{} & \\
    \hline
  \end{tabular}
  \caption{Details of the datasets employed for train and test.}
  \label{T:dataset_details}
\end{table*}

\section{Experiments}
We conduct a number of experiments to explore the performance of our method. First we exploit a number of widely available vehicle ID benchmark datasets in order to assess the benefit of each of the branches of our model independently, and altogether. Then we compare the performance of our model to other current work by looking at our performance in the NVIDIA AI City Challenge 2019 Task 2 (Vehicle Re-identification). As our method includes a branch that predicts vehicle orientation in addition to identity, our model requires data that contains the orientation labels for training. As a result, we include the VeRI776 \cite{liu2016veri} dataset in the training set for all our experiments.

@@

\subsection{Implementation Details}
We employ the ResNet50 \cite{} network architecture as the base of our model. We train the model with minibatches of size 8, using the Adam optimisation technique with a learning rate of 0.0001, exponential decay rates set as follows: $\beta_1=0.9$ and $\beta_2=0.999$. The two image sizes used were standard $224\x224$ and small (for the scaled branch) $160\x160$.

@@

\subsection{Evaluation on Veri776 Dataset}
We train and test only the VeRi776 dataset, for comparison with previous state-of-the-art methods.
Table \ref{T:benchmark_results_veri} shows the results of the first experiment, where we train and test only on the VeRi776 dataset. All experiments we continued for 150 epochs of training. As can be seen, even before re-ranking, our full model achieves state-of-the-art mAP and Rank-1 scores on this dataset, of 64.6\% and 92.3\% respectively. And after re-ranking the mAP score is increased to an impressive 68.3\%.
%\textcolor{red}{TODO more detailed discussion of results}

\subsection{Evaluation on VehicleID Dataset}
We train on both the VeRi776 and VehicleID datasets, and then test on the VehicleID, for all three testsets: small, medium and large. We conduct the latter experiment in this was due to the fact that our method requires some training data with orientation labels. As VeRi776 is the only dataset with labels of this kind, we must therefore include it in the training.

\textcolor{red}
{
Table \ref{T:benchmark_results_vehicleid} shows that ...
(Please add some comparison methods in Table 3)
}

\begin{table}
  \centering
  \begin{tabular}{l || c | c | c }
    \hline
    Method & mAP & Rank-1 & Rank-5 \\
    \hline
    MSVF \cite{kanaci2018vehicle} & 49.3 & 88.6 & - \\
    OIFE \cite{wang2017orientation} & 51.4 & 68.3 & 89.7 \\
    S-CNN+P-LSTM \cite{Shen_2017_ICCV} & 58.3 & 83.5 & 90.0 \\
    MTCRO \cite{xu2018framework} & 61.6 & 87.2 & 94.2 \\
    MTCRO (ReRank) \cite{xu2018framework} & 62.6 & 88.0 & 94.6 \\
    \hline
    MTML-S & 59.4 & 89.5 & 94.9 \\
    MTML-O & 60.8 & 90.2 & 95.4 \\
    MTML-G & 62.8 & 91.1 & 95.8 \\
    \hline
    MTML-SG & 63.7 & 90.6 & 95.8 \\
    MTML-OG & 63.5 & 92.0 & \bf{96.4}\\
    MTML-OSG & \bf{64.6} & \bf{92.3} & 95.7 \\
    MTML-OSG (ReRank) & \bf{\emph{68.3}} & 92.0 & 94.2 \\
    \hline
  \end{tabular}
  \caption{Trained/tested on VeRi776 only}
  \label{T:benchmark_results_veri}
\end{table}

\begin{table}
  \centering
  \setlength{\tabcolsep}{0.01cm}
  \begin{tabular}{l || c | c || c | c || c | c }
    \hline
    \multirow{2}{*}{Method} & \multicolumn{2}{c}{Small} & \multicolumn{2}{c}{Medium} &\multicolumn{2}{c}{Large} \\
    \cline{2-7}
    & mAP & Rank-1 & mAP & Rank-1 & mAP & Rank-1 \\
    \hline
    MTML-S & \\
    MTML-O & \\
    MTML-G & \\
    % \hdashline
    MTML-SG & \\
    MTML-OG & \\
    MTML-OSG & \\
    % \hdashline
    MTML-OSG+ReRank & \\
    \hline
  \end{tabular}
  \caption{Trained on VeRi776+VehicleID, tested on VehicleID}
  \label{T:benchmark_results_vehicleid}
\end{table}

@@

\begin{table}[ht]
  \centering
  \begin{tabular}{l || c | c | c }
    \hline
    Method & mAP & Rank-1 & Rank-5 \\
    \hline
    MSVF \cite{kanaci2018vehicle} & & & \\
    MTCRO (ReRank) \cite{xu2018framework} &  & & \\
    \hline
    MTML-S &  & & \\
    MTML-G & 19.7 & 44.6 & 58.5 \\
    \hline
    MTML-SG & 20.6 & 44.2 & 55.8 \\
    \hline
    MTML-SG (ReRank) &  & & \\
    \hline
  \end{tabular}
  \caption{Trained/tested on CityFlow}
  \label{T:cityflow_results}
\end{table}

\begin{table}[ht]
  \centering
  \setlength{\tabcolsep}{0.01cm}
  \begin{tabular}{l|c|c|c|c|c|c}
  \hline
  \multicolumn{1}{r|}{Test:} & \multicolumn{3}{c|}{VeRi-776} & \multicolumn{3}{c}{CityFlow} \\
  \hline
  Method       & mAP    & Rank-1   & Rank-5   & mAP    & Rank-1   & Rank-5   \\
  \hline
  MTML-S       &        &          &          &        &          &          \\
  MTML-O       &        &          &          &        &          &          \\
  MTML-G       &        &          &          &        &          &          \\
  MTML-SG      &        &          &          &        &          &          \\
  MTML-OG      &        &          &          &        &          &          \\
  MTML-OSG     &        &          &          &        &          &      \\
  \hline
  \end{tabular}
  \caption{Trained/tested on CityFlow+VeRi-776}
  \label{T:cf_veri_res}
\end{table}

@@

\section{Conclusions}
Due to the main challenge of vehicle Re-ID: the visual appearance of vehicles may drastically changes
according to diverse viewpoints and illumination.
%
In this paper, we propose a novel {\em Multi-Task Mutual Learning} (MTML) deep model
to learn discriminative feature simultaeously from multiple branches.
%
Specially, we design a consensus learning loss function by fusing feature of the final convolutional feature maps from all branches.
%
Extensive comparative evaluations demonstrate the effectiveness of the
proposed MTML method in comparison to the state-of-the-art vehicle Re-ID techniques on the two existing benchmarks
(VehicleID and VeRi-776).
We also get a competitive result on NVIDIA 2019 AI City Challenge Track 2.

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
Vehicle re-identification (Re-ID) aims to search a specific vehicle
instance across non-overlapping camera views.
%
The main challenge of vehicle Re-ID is that
the visual appearance of vehicles may drastically changes
according to diverse viewpoints and illumination.
%
Most of existing vehicle Re-ID model cannot make full use of
various complementary vehicle information, e.g. vehicle type and orientation.
%
In this paper, we propose a novel {\em Multi-Task Mutual Learning} (MTML) deep model
to learn discriminative feature simultaeously from multiple branches.
%
Specially, we design a consensus learning loss function by fusing feature of the final convolutional feature maps from all branches.
%
Extensive comparative evaluations demonstrate the effectiveness of the
proposed MTML method in comparison to the state-of-the-art vehicle Re-ID techniques on the two existing benchmarks
(VehicleID and VeRi-776).
We also yield competitive performance on the NVIDIA 2019 AI City Challenge Track 2.
\end{abstract}

@@

%% Background of vehicle Re-ID
With the development of autonomous driving
and smart city applications, the need for accurately analyzing vehicles on urban streets 
by incorporating all the necessary computer vision tasks including detection, classification and
pose estimation as well as re-identification is ever-increasing.
%
Specially, vehicle re-identification attracted increasing attentions in the research community
\cite{liu2016vehicleid,liu2016veri,liu2016veri,
wang2017orientation,Wang_2017_ICCV,Zhou2018VAMI},
since it can play an important role in
intelligent transportation systems and public safety.

%% What's vehicle Re-ID?
Vehicle re-identification (Re-ID) aims at searching a specific vehicle
instance across non-overlapping camera views.
%
Due to the unavailability of license plate under uncontrolled view angles,
vehicle Re-ID by visual appearance is of great practical value in real-world applications such as smart cities.
%
This task is similar with a more popular task: person re-identification
\cite{gong2014re,chen2018person,Li2018Harmonious,xiao2016learning,
li2017person,wei2018person,song2018mask,chang2018multi,
shen2018deep,zhang2017deep,shen2018person,suh2018part},
but with more challenges:
%% Vehicle Re-ID challenges
(1) Unlike person Re-ID, pose/orientation of vehicles results in occlusion and drastic visual geometry changes, since vehicle is a kind of rigid body.
% The same vehicle under different viewpoints are visually more diverse than person,
This means that the same identity must be inferred with any given pose/orientation of a vehicle.
(2) Even in the same orientation, vehicles of different identities may look very similar
due to the same vehicle model. This requires vehicle Re-ID models
to have a more discriminative fine-grained recognition ability.

% Existing work's problem
Most of vehicle Re-ID methods \cite{liu2016vehicleid,liu2016veri,Shen_2017_ICCV,Zhou2018VAMI}
focus on using a single branch
to learn an embedding feature for vehicle instance re-identification
from the original information (e.g. the original whole vehicle image).
%
Due to the previously metioned challenges for vehicle re-identification,
this single branch structure can not take advantage of the diversity of vehicles.
%
Moreover, most existing works
\cite{liu2016vehicleid,liu2016veri}
train vehicle Re-ID deep learning model
using a single supervisory signal (e.g. vehicle ID).
%
However, vehicle ID label {\em alone} can not differentiate the differences between vehicles due to:
(1) vehicle instances of the same ID under different viewpoints,
(2) vehicle instances of different IDs under the same viewpoint.
We suggest that imposing multiple and different supervisory signals
simultaneously (e.g. vehicle ID and vehicle orientation) is more effective
for learning more fine-grained discriminative features for vehicle
Re-ID.

%\begin{figure}
%%  \includegraphics[width=\linewidth,trim=0cm 8cm 0cm 0cm,clip=true]{images/system_overview_orient_only.pdf}
%  \caption{A comparision of the same vehicle ID and different ID.}
%	\label{F:veh_comparison}
%\end{figure}

% Our contributions
In this work, we propose a novel {\em Multi-Task Mutual Learning}
(MTML) based network architecture,
that aims to simultaneously learn a number of recognition tasks from
different supervisory signals, plus a consensus loss function, to
build an improved representation for the purpose of vehicle
re-identification.

We make two contributions in this work as follows:
(1) We formulate a novel {\em Multi-Task Mutual Learning} (MTML) deep
learning model by building each individual branch for a different
recognition task relevant to vehicle Re-ID and by taking into
consideration different four tasks including vehicle ID, multi-scale, grayscale, and orientation.
Our model aims to discover and capture concurrently complementary discriminative information.
(2) We introduce a mutual learning mechanism for improving multi-task learning robustness.
Our model benefits from multiple supervisory signals in order to
enhance model learning of more discrimative features for vehicle Re-ID.
%(3) we propose a cross-dataset joint learning framework for vehicle Re-ID.
Extensive comparative evaluations demonstrate the effectiveness of the
proposed MTML method in comparison to the state-of-the-art vehicle Re-ID techniques on the two existing benchmarks
(VehicleID \cite{liu2016vehicleid} and VeRi-776 \cite{liu2016veri}).
We also yield competitive performance on the CityFlow
\cite{tang2019cityflow} benchmark at the NVIDIA 2019 AI City Challenge.

@@

\noindent {\bf Vehicle Model Classification }
One closely related problem to re-identification is vehicle model
classification
\cite{liao2015exploiting,yang2015compcars,sochor2016boxcars,hu2017deep}.
The two problems are usually studied independently.
For example, Yang et al. \cite{yang2015compcars} propose a part attributes driven
vehicle model recognition.
They also contribute a large comprehensive car dataset named ``CompCars''
with model class labels but without vehicle identity labels.
More recently, Hu et al. \cite{hu2017deep} formulate a deep CNN framework capable of
selecting spatial salient vehicle parts in order to learn more
discriminative model representations without explicit parts annotations.

\noindent {\bf Vehicle Re-Identification. }
%Whist vehicle Re-ID is less studied than person Re-ID
%\cite{gong2014person,li2018harmonious,zhong2017camera},
%there are a handful of existing methods.
%Notably, Feris \etal \cite{feris2012large} proposed an attribute-based Re-ID method.
%The vehicles are firstly classified by different attributes like car model types and colours. The Re-ID matching is then conducted in the attribute space.
%%
%Dominik \etal \cite{zapletal2016vehicle}
%used 3D bounding boxes for rectifying car images and then concatenate colour histogram features of vehicle image pairs.
%A binary linear SVM model is then trained to verify whether a pair of images have the same identity.
%%
%Both methods rely heavily on weak hand-crafted visual features in a
%complex multi-step based approach, suffering from weak discriminative model generalisation.
Deep learning techniques have been exploited to vehicle Re-ID. For instance, Liu
\etal \cite{liu2016veri} explored a deep neural network to estimate the
visual similarities between vehicle images.
%Vehicle appearances, spatio-temporal information and license plates are
%independently and incrementally used to improve the similarity function for
%vehicle matching.  they use a deep neural network to estimate the visual
%similarities between vehicle images for enjoying the strong representation
%learning capacity.
%
Liu \etal \cite{liu2016vehicleid} also designed a Coupled Clusters Loss (CCL)
to boost a multi-branch CNN model for vehicle Re-ID.
%
All these methods utilize the global appearance features of vehicle images and
ignore local discriminative regions.
%
To explore local information motivated by the idea of landmark alignment
\cite{zhang2014facial} in both face recognition \cite{taigman2014deepface} and
human body pose estimation \cite{newell2016stacked}, Wang \etal
\cite{Wang_2017_ICCV} considered 20 vehicle keypoints for learning and aligning
local regions of a vehicle for Re-ID.  Clearly, this approach comes with extra
cost of exhaustively labeling these keypoints in a large number of vehicle
images, and the implicit assumption of having sufficient image
resolution/details for extracting these keypoints.
%

@@

\noindent{\bf Multi-Task Learning. }
Multi-task learning (MTL) is a machine learning strategy
that learns several related tasks simultaneously for
their mutual benefits \cite{argyriou2007multi}. %  \cite{evgeniou2004regularized,ando2005framework,argyriou2007multi}.
A good MTL survey with focus on neural networks
is provided in \cite{caruana1997multitask}.
%
Deep CNNs are well suited for
performing MTL as they are inherently designed to learn joint
feature representations subject to multiple label objectives
concurrently in multi-branch architectures.
%
Joint learning of multiple related tasks
has been proven to be effective in solving computer vision problems
\cite{dong2017multi,zhang2016learning}.
% \cite{dong2017multi,zhang2016learning,ahmed2008training}.
%
Critically, our method is uniquely designed to
explore the potential of MTL
in combining multiple diversities (e.g. scale and color) of the vechile image
and being supervised by multiple kinds of manual labels (e.g. ID and orientation).
Each of them is associated with an individual branch of a single model.

@@

An overview of our proposed model can be seen in Figure
\ref{F:overview}. The model is composed of four sub-branches, each of
which is simultaneously learning a representation to solve its own
task. In addition, there is a single fusion branch, which allows
feature selection to be performed from the entire collection of
individual representations. It is the output from this branch that is
taken during deployment. Each sub-branch will now be described in more
detail.

@@

In order to encourage the model to focus on details of the vehicles,
that allow for separation of highly similar identity classes, we
ensure that one branch will be unable to use colour information for
distinguishing between these classes. This is done by giving as input
only the grayscale image, and again training the branch to predict
identity via the cross entropy loss.

@@

This branch is tasked with learning a representation to simultaneously
predict the identity class and the orientation class when this is known.
%In the case where the training images do not have associated orientation labels, this branch is trained in exactly the same way as the Vehicle Identity branch outlined above.
Both sets of labels are simultaneously employed in a joint loss function in order to optimise the branch for prediction of both identity and orientation. As orientation labels are not available for all training data, we employ a selective classifcation subset loss function, that allows the loss to be calculated across only the subset of the batch for which orientation labels are known.

@@

\begin{table*}
  \centering
  \begin{tabular}{c || c | c | c || c | c || c | c}
    \hline
    \multirow{2}{*}{Dataset} & \multicolumn{3}{c||}{Training} & \multicolumn{2}{c||}{Probe} & \multicolumn{2}{c}{Gallery} \\
    \cline{2-8}
    & \#IDs& \#Imgs & \#Orients & \#IDs & \#Imgs & \#IDs & \#Imgs \\
    \hline
    VeRi-776 \cite{liu2016veri}
    & 576 & 37778 & 8 & 200 & 1678 & 200 & 11579 \\
%     VehicleID \cite{liu2016vehicleid}
%     & 13164 & 100182 & - & 2400 & 17638 & 2400 & 2400 \\
%    BoxCars \cite{} & 21250 & 63750 & -  & - & - & - & - \\
%    CompCars \cite{} & 1118 & 31148 & - & - & - & - & - \\
    CityFlow \cite{tang2019cityflow} 
    & 333 & 36935 & - & 333 & 1052 & 333 & 18290 \\
    \hline
  \end{tabular}
  \caption{Details of the datasets employed for train and test.}
  \label{T:dataset_details}
\end{table*}

\section{Experiments}

\begin{table}[h]
  \centering
  \begin{tabular}{l || c | c | c }
    \hline
    Method & mAP & Rank-1 & Rank-5 \\
    \hline
    MSVF \cite{kanaci2018vehicle} & 49.3 & 88.6 & - \\
    OIFE \cite{wang2017orientation} & 51.4 & 68.3 & 89.7 \\
    S-CNN+P-LSTM \cite{Shen_2017_ICCV} & 58.3 & 83.5 & 90.0 \\
    MTCRO \cite{xu2018framework} & 61.6 & 87.2 & 94.2 \\
    MTCRO (ReRank) \cite{xu2018framework} & 62.6 & 88.0 & 94.6 \\
    \hline
    MTML-S & 59.4 & 89.5 & 94.9 \\
    MTML-O & 60.8 & 90.2 & 95.4 \\
    MTML-G & 62.8 & 91.1 & 95.8 \\
    \hline
    MTML-SG & 63.7 & 90.6 & 95.8 \\
    MTML-OG & 63.5 & 92.0 & \bf{96.4}\\
    MTML-OSG & \bf{64.6} & \bf{92.3} & 95.7 \\
    MTML-OSG (ReRank) & \bf{\emph{68.3}} & 92.0 & 94.2 \\
    \hline
  \end{tabular}
  \caption{Trained/tested on VeRi776 only}
  \label{T:benchmark_results_veri}
\end{table}

We conduct a number of experiments to explore the performance of our method. First we exploit a number of widely available vehicle ID benchmark datasets in order to assess the benefit of each of the branches of our model independently, and altogether. Then we compare the performance of our model to other current work by looking at our performance in the NVIDIA AI City Challenge 2019 Task 2 (Vehicle Re-identification). As our method includes a branch that predicts vehicle orientation in addition to identity, our model requires data that contains the orientation labels for training. As a result, we include the VeRI776 \cite{liu2016veri} dataset in the training set for all our experiments.

@@

\subsection{Implementation Details}
We employ the ResNet50 \cite{} ({\bf SG: missing reference}) network
architecture as the base of our model. We train the model with
minibatches of size 8, using the Adam optimisation technique with a
learning rate of 0.0001, exponential decay rates set as follows:
$\beta_1=0.9$ and $\beta_2=0.999$. The two image sizes used were
standard $224\x224$ and small (for the scaled branch) $160\x160$.

@@

\subsection{Evaluation on the Veri776 Dataset}
First, we train and test on the VeRi776 dataset so to compare with
existing state-of-the-art methods on identical settings.
Table \ref{T:benchmark_results_veri} shows the results of the first
experiment, where we train and test only on the VeRi776 dataset. All
experiments we continued for 150 epochs of training. As can be seen,
even before re-ranking, our full model achieves state-of-the-art mAP
and Rank-1 scores on this dataset, of 64.6\% and 92.3\%
respectively. And after re-ranking the mAP score is increased to an
impressive 68.3\%. 
%\textcolor{red}{TODO more detailed discussion of results}

\subsection{Evaluation on the VehicleID Dataset}
Second, we then train on both the VeRi776 and VehicleID datasets, and
test on VehicleID with all three of its test sets: small, medium and
large. We conducted this experiment to explore the benefit of training
model using additional orientation labels, as VeRi776 is the only
dataset available with orientation labels.

\textcolor{red}
{
Table \ref{T:benchmark_results_vehicleid} shows that ...
(Please add some comparison methods in Table 3)
}
({\bf SG: missing results})

%\begin{table}
%  \centering
%  \setlength{\tabcolsep}{0.01cm}
%  \begin{tabular}{l || c | c || c | c || c | c }
%    \hline
%    \multirow{2}{*}{Method} & \multicolumn{2}{c}{Small} & \multicolumn{2}{c}{Medium} &\multicolumn{2}{c}{Large} \\
%    \cline{2-7}
%    & mAP & Rank-1 & mAP & Rank-1 & mAP & Rank-1 \\
%    \hline
%    MTML-S & \\
%    MTML-O & \\
%    MTML-G & \\
%    % \hdashline
%    MTML-SG & \\
%    MTML-OG & \\
%    MTML-OSG & \\
%    % \hdashline
%    MTML-OSG+ReRank & \\
%    \hline
%  \end{tabular}
%  \caption{Trained on VeRi776+VehicleID, tested on VehicleID}
%  \label{T:benchmark_results_vehicleid}
%\end{table}

@@

\begin{table}[h]
  \centering
  \begin{tabular}{l || c | c | c }
    \hline
    Method & mAP & Rank-1 & Rank-5 \\
    \hline
    Resnet50\cite{tang2019cityflow} & 25.5 & 41.3 & - \\
    \hline
    MTML-S  & 17.0 & 40.4 & 53.3 \\
    MTML-G  & 19.6 & 44.5 & 58.4 \\
    \hdashline
    MTML-SG & 20.6 & 44.1 & 55.8 \\
    \hdashline
    MTML-SG (ReRank) &  & & \\
    \hline
  \end{tabular}
  \caption{Trained/tested on CityFlow}
  \label{T:cityflow_results}
\end{table}

\begin{table}[h]
  \centering
  \setlength{\tabcolsep}{0.05cm}
  \begin{tabular}{l|c|c|c|c|c|c}
  \hline
  \multicolumn{1}{r|}{Test:} & \multicolumn{3}{c|}{VeRi-776} & \multicolumn{3}{c}{CityFlow} \\
  \hline
  Method       & mAP   & Rank-1  & Rank-5  & mAP   & Rank-1 & Rank-5  \\
  \hline
  MTML-O       &       &         &         &       &        &         \\
  MTML-S       &       &         &         &       &        &         \\
  MTML-G       & 61.6  & 89.7    & 95.1    &       &        &         \\
  MTML-SG      & 62.6  & 90.8    & 95.8    &       &        &         \\
  MTML-OG      &       &         &         &       &        &         \\
  MTML-OSG     &       &         &         &       &        &      \\
  \hline
  \end{tabular}
  \caption{Trained/tested on CityFlow+VeRi-776}
  \label{T:cf_veri_res}
\end{table}

@@

\section{Conclusions}
Vehicle Re-ID is difficult because the visual appearance of
a vehicle instance may drastically change due to diverse
viewpoints and illumination, whilst different vehicle instances of the same
model type may have a very similar appearance.
%
In this paper, we propose a novel {\em Multi-Task Mutual Learning} (MTML) deep model
to learn discriminative feature simultaeously from multiple branches.
%
Moreover, we design a consensus learning loss function by fusing feature of the final convolutional feature maps from all branches.
%
Extensive comparative evaluations demonstrate the effectiveness of the
proposed MTML method in comparison to the state-of-the-art vehicle Re-ID techniques on the two existing benchmarks
(VehicleID and VeRi-776).
We also yield a competitive performance on the NVIDIA 2019 AI City Challenge Track 2.
